---
title: "Usage & tips"
author: "John Coene"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage & tips}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Name Tagging

* `<END>.` is *invalid*
* `<END> .` is *valid*

Use `check_tags` to make sure they are correct.

## Tagger

A *currently* basic tagger to easily tag training data to train a token name finder (`tnf_train`).

```r
# Manually tagged
manual <- paste("This organisation is called the <START:wef> World Economic Forum <END>",
              "It is often referred to as <START:wef> Davos <END> or the <START:wef> WEF <END> .")

# Create untagged string              
data <- paste("This organisation is called the World Economic Forum",
  "It is often referred to as Davos or the WEF.")

# tag string
auto <- tag_docs(data, "WEF", "wef")
auto <- tag_docs(auto, "World Economic Forum", "wef")
auto <- tag_docs(auto, "Davos", "wef")

identical(manual, auto)
```

## Training data

### Token name finder

You will need considerable training data for the name extraction; 15'000 sentences. However, this does not mean 15'000 tagged sentences, this means 15'000 sentences representative of the documents you will have to extract names from.

Including sentences that do not contain tagged names reduces false positives; *the model learns what to extract as much as it learns what not to extract.*

### Document classifier

In order to train a decent document classifier you are going to need 5'000 classified documents as training data with a *bare* minimum of 5 documents per category.

```{r}
library(decipher)

# get working directory
# need to pass full path
wd <- getwd()

data <- data.frame(
  class = c("Sport", "Business", "Sport", "Sport", "Business", "Politics", "Politics", "Politics"),
  doc = c("Football, tennis, golf and, bowling and, score.",
          "Marketing, Finance, Legal and, Administration.",
          "Tennis, Ski, Golf and, gym and, match.",
          "football, climbing and gym.",
          "Marketing, Business, Money and, Management.",
          "This document talks politics and Donal Trump.",
          "Donald Trump is the President of the US, sadly.",
          "Article about politics and president Trump.")
)

# Error not enough data
model <- dc_train(model = paste0(wd, "/model.bin"), data = data, lang = "en")

Sys.sleep(15)

# repeat data 50 times
# Obviously do not do that in te real world
data <- do.call("rbind", replicate(50, data[sample(nrow(data), 4),],
                                   simplify = FALSE))

# train model
model <- dc_train(model = paste0(wd, "/model.bin"), data = data, lang = "en")
```
